% Acknowledge those who helped and supported you
\Acknowledgments{
First, I would like to express my sincere acknowledgement to my adivsor and
teacher, Prof. Gal A. Kaminka who encouraged and challenged me through my
academic years.
Gal never accepted less than my best efforts. I learned from him a lot about the
art of conducting a research, writing an academic paper, giving a presentation
(highly recommended tips can be found in his site!) and of course, the art of
mingling.
Gal also gave me the opportunity to gain a management experience by assigning me
as team leader of our lab's RoboCup soccer team.
Moreover, being Gal's student enabled me to discover the
mysterious limits of the human body combined with coffee and a deadline.
Thank you for being the greatest advisor of all!

I wish to thank Gabriella Melamed, our lab manager and one of my best
friends. She always makes me see things in a new point of view. 
In addition, she is an amazing cook and that definitely helped me to come up
with new ideas. 

Many thanks to Sharon Handzel-Yalov for giving me the boost with the complexity
analysis proofs. Thank you for your time.

I wish to thank my family who have always supported me. Words alone cannot
express what I owe them for their encouragement and whose patient love enabled
me to complete this thesis.

I also wish to thank Kai M. Wurm and Wolfram Burgard for 
providing us with their code.
Thanks go to Cyrill Stachniss, Giorgio Grisetti and Nick
Roy for providing data to the Robotics Data Set Repository
(Radish).  

Last but not least, I would like to express my sincere thanks to my friends and
colleagues for the great time we had together and would have in the future, for
sure. 

This research was partially supported by ISF grant \#1357/07 and MAFAT.
}